An Accurate Model for SARS-CoV-2 Pooled RT-PCR Test Errors

### 2021-09-15 paper.tex
all in 1

\documentclass{article}
\input{definitions}

@@

\bibliographystyle{amsplain}
\bibliography{refs}

@@

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{marginnote}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=red,linkcolor=red,bookmarks=true]{hyperref}
\usepackage{soul}
%% \usepackage{pgfplots}
%% \pgfplotsset{compat=1.14}
%% \usepackage{tikz}
%% \usetikzlibrary{arrows.meta}
%% \usetikzlibrary{shapes.geometric}
%% \usetikzlibrary{bayesnet} 
\usepackage{float}
\usepackage{geometry}
\hypersetup{linkcolor=red,citecolor=green,urlcolor=blue}

\newcommand{\fp}{P_{\text{fp}}}
\newcommand{\fn}{P_{\text{fn}}}
\newcommand{\Se}{S_\text{e}}
\newcommand{\Sp}{S_\text{p}}
\newcommand{\mi}{S_{\text{fn}}}
\newcommand{\err}[1]{E_{\text{{#1}}}}%_{\text{rel}}}
\newcommand{\eff}[1]{E_{\text{{#1}}}}%_{\text{rel}}}
\renewcommand\Affilfont{\itshape\small}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\data}{\mathbf{d}}
\newcommand{\sens}{S_{\text{e}}}
\newcommand{\spec}{S_{\text{p}}}
% \newcommand{\tn}{P_{\text{tn}}}

@@

\bibliographystyle{amsplain}
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{10}

\bibitem{OptimalDorfmanPool}
Hrayer Aprahamian, Douglas~R Bish, and Ebru~K Bish, \emph{Optimal group
  testing: Structural properties and robust solutions, with application to
  public health screening}, INFORMS Journal on Computing (2020).

\bibitem{DorfmanYuvalDor}
Netta Barak, Roni Ben-Ami, Tal Sido, Amir Perri, Aviad Shtoyer, Mila Rivkin,
  Tamar Licht, Ayelet Peretz, Judith Magenheim, Irit Fogel, et~al.,
  \emph{Lessons from applied large-scale pooling of 133,816 {SARS-CoV}-2
  {RT-PCR} tests}, Science Translational Medicine (2021).

\bibitem{Simplistic2}
Alhaji Cherif, Nadja Grobe, Xiaoling Wang, and Peter Kotanko, \emph{Simulation
  of pool testing to identify patients with coronavirus disease 2019 under
  conditions of limited test availability}, JAMA network open \textbf{3}
  (2020), no.~6, e2013075--e2013075.

\bibitem{DOPE}
Yair Daon, Amit Huppert, and Uri Obolsik, \emph{{DOPE}: {D}-{O}ptimal {P}ooling
  {E}xperimental design with application to {SARS-CoV}-2 screening}, {arXiv}
  (2021).

\bibitem{JTM}
Yair Daon, Robin~N Thompson, and Uri Obolski, \emph{Estimating covid-19
  outbreak risk through air travel}, Journal of Travel Medicine \textbf{27}
  (2020), no.~5, taaa093.

\bibitem{Salazar}
Adolfo de~Salazar, Antonio Aguilera, Rocio Trastoy, Ana Fuentes, Juan~Carlos
  Alados, Manuel Causse, Juan~Carlos Gal{\'a}n, Antonio Moreno, Matilde Trigo,
  Mercedes P{\'e}rez-Ruiz, et~al., \emph{Sample pooling for {SARS-CoV-2 RT-PCR}
  screening}, Clinical Microbiology and Infection \textbf{26} (2020), no.~12,
  1687.e1--1687.e5.

\bibitem{PoolingAirports}
Philip Dollard, Isabel Griffin, Andre Berro, Nicole~J Cohen, Kimberly Singler,
  Yoni Haber, Chris de~la Motte~Hurst, Amber Stolp, Sukhshant Atti, Leslie
  Hausman, et~al., \emph{Risk assessment and management of covid-19 among
  travelers arriving at designated us airports, january 17--september 13,
  2020}, Morbidity and Mortality Weekly Report \textbf{69} (2020), no.~45,
  1681.

\bibitem{DorfmanOriginal}
Robert Dorfman, \emph{The detection of defective members of large populations},
  The Annals of Mathematical Statistics \textbf{14} (1943), no.~4, 436--440.

\bibitem{RecursiveSevenFold}
Jens~Niklas Eberhardt, Nikolas~Peter Breuckmann, and Christiane~Sigrid
  Eberhardt, \emph{Multi-stage group testing improves efficiency of large-scale
  {COVID}-19 screening}, Journal of Clinical Virology \textbf{128} (2020),
  104382.

\bibitem{CherifReview}
Nadja Grobe, Alhaji Cherif, Xiaoling Wang, Zijun Dong, and Peter Kotanko,
  \emph{Sample pooling: burden or solution?}, Clinical Microbiology and
  Infection (2021).

\bibitem{LionDorfman}
Rudolf Hanel and Stefan Thurner, \emph{Boosting test-efficiency by pooled
  testing for {SARS-CoV}-2---{F}ormula for optimal pool size}, PLoS One
  \textbf{15} (2020), no.~11, e0240652.

\bibitem{DilutionCOVID}
Yosuke Hirotsu, Makoto Maejima, Masahiro Shibusawa, Yuki Nagakubo, Kazuhiro
  Hosaka, Kenji Amemiya, Hitomi Sueki, Miyoko Hayakawa, Hitoshi Mochizuki,
  Toshiharu Tsutsui, et~al., \emph{Pooling {RT-qPCR} testing for {SARS-CoV-2}
  in 1000 individuals of healthy and infection-suspected patients}, Scientific
  reports \textbf{10} (2020), no.~1, 1--8.

\bibitem{MassPooling}
Ed~Holt, \emph{Slovakia to test all adults for sars-cov-2}, The Lancet
  \textbf{396} (2020), no.~10260, 1386--1387.

\bibitem{GroupDilution}
Frank~K Hwang, \emph{Group testing with a dilution effect}, Biometrika
  \textbf{63} (1976), no.~3, 671--680.

\bibitem{Kim}
Hae-Young Kim, Michael~G Hudgens, Jonathan~M Dreyfuss, Daniel~J Westreich, and
  Christopher~D Pilcher, \emph{Comparison of group testing algorithms for case
  identification in the presence of test errors}, Biometrics \textbf{63}
  (2007), no.~4, 1152--1163.

\bibitem{EstimatingRatesKucrika}
Lauren~M Kucirka, Stephen~A Lauer, Oliver Laeyendecker, Denali Boon, and Justin
  Lessler, \emph{Variation in false-negative rate of reverse transcriptase
  polymerase chain reaction---based {SARS-CoV}-2 tests by time since exposure},
  Annals of Internal Medicine (2020).

\bibitem{MatrixPooling}
Thomas~J Kwiatkowski~Jr, Huda~Y Zoghbi, Susan~A Ledbetter, Kimberly~A Ellison,
  and A~Craig Chinault, \emph{Rapid identification of yeast artificial
  chromosome clones by matrix pooling and crude lysate {PCR}.}, Nucleic acids
  research \textbf{18} (1990), no.~23, 7191.

\bibitem{PoolSize30}
Stefan Lohse, Thorsten Pfuhl, Barbara Berk{\'o}-G{\"o}ttel, J{\"u}rgen
  Rissland, Tobias Gei{\ss}ler, Barbara G{\"a}rtner, S{\"o}ren~L Becker, Sophie
  Schneitler, and Sigrun Smola, \emph{Pooling of samples for testing for
  {SARS}-{C}o{V}-2 in asymptomatic people}, The Lancet Infectious Diseases
  (2020).

\bibitem{MinaScience}
Michael~J Mina and Kristian~G Andersen, \emph{{COVID}-19 testing: {O}ne size
  does not fit all}, Science \textbf{371} (2021), no.~6525, 126--127.

\bibitem{BayesianDorfman}
Rodrigo Noriega and Matthew Samore, \emph{Increasing testing throughput and
  case detection with a pooled-sample {B}ayesian approach in the context of
  {COVID}-19}, bioRxiv (2020).

\bibitem{TestingAirportsJapan}
Masataro Norizuki, Masahiko Hachiya, Ayano Motohashi, Ataru Moriya, Kazuhisa
  Mezaki, Moto Kimura, Wataru Sugiura, Hidechika Akashi, and Tamami Umeda,
  \emph{Effective screening strategies for detection of asymptomatic covid-19
  travelers at airport quarantine stations: Exploratory findings in japan},
  Global Health \& Medicine (2021), 2020--01109.

\bibitem{Simplistic1}
Alexander Pikovski and Kajetan Bentele, \emph{Pooling of coronavirus tests
  under unknown prevalence}, Epidemiology \& Infection \textbf{148} (2020).

\bibitem{CompressedPooling}
Noam Shental, Shlomia Levy, Vered Wuvshet, Shosh Skorniakov, Bar Shalem, Aner
  Ottolenghi, Yariv Greenshpan, Rachel Steinberg, Avishay Edri, Roni Gillis,
  et~al., \emph{Efficient high-throughput {SARS-CoV}-2 testing to detect
  asymptomatic carriers}, Science advances \textbf{6} (2020), no.~37, eabc5961.

\bibitem{PoolSchool}
Catherine~M Sweeney-Reed, Doreen Wolff, Jakob Niggel, Michael Kabesch, and
  Christian Apfelbacher, \emph{Pool testing as a strategy for prevention of
  sars-cov-2 outbreaks in schools: Protocol for a feasibility study}, JMIR
  Research Protocols \textbf{10} (2021), no.~5, e28673.

\bibitem{RobinHood}
Robin~N Thompson, Francesca~A Lovell-Read, and Uri Obolski, \emph{Time from
  symptom onset to hospitalisation of coronavirus disease 2019 ({COVID-19})
  cases: implications for the proportion of transmissions from infectors with
  few symptoms}, Journal of clinical medicine \textbf{9} (2020), no.~5, 1297.

\bibitem{KitComparison}
Puck~B van Kasteren, Bas van Der~Veer, Sharon van~den Brink, Lisa Wijsman,
  J{\o}rgen de~Jonge, Annemarie van~den Brandt, Richard Molenkamp, Chantal~BEM
  Reusken, and Adam Meijer, \emph{Comparison of seven commercial {RT-PCR}
  diagnostic kits for {COVID}-19}, Journal of Clinical Virology \textbf{128}
  (2020), 104412.

\bibitem{InterpretingCOVID19Test}
Jessica Watson, Penny~F Whiting, and John~E Brush, \emph{Interpreting a
  {COVID}-19 test result}, {BMJ} \textbf{369} (2020).

\bibitem{DilutionHIV}
Lawrence~M Wein and Stefanos~A Zenios, \emph{Pooled testing for {HIV}
  screening: capturing the dilution effect}, Operations Research \textbf{44}
  (1996), no.~4, 543--569.

\bibitem{EstimatingRatesLourenco}
Paul~S Wikramaratna, Robert~S Paton, Mahan Ghafari, and Jos{\'e}
  Louren{\c{c}}o, \emph{Estimating the false-negative test probability of
  {SARS-CoV}-2 by {RT-PCR}}, Eurosurveillance \textbf{25} (2020), no.~50,
  2000568.

\bibitem{FalsePositiveEstimate}
Steven Woloshin, Neeraj Patel, and Aaron~S Kesselheim, \emph{False negative
  tests for {SARS}-{C}o{V}-2 infection-challenges and implications}, New
  England Journal of Medicine (2020).

\bibitem{Lion}
Idan Yelin, Noga Aharony, Einat~Shaer Tamar, Amir Argoetti, Esther Messer, Dina
  Berenbaum, Einat Shafran, Areen Kuzli, Nagham Gandali, Omer Shkedi, et~al.,
  \emph{Evaluation of {COVID-19 RT-qPCR} test in multi sample pools}, Clinical
  Infectious Diseases \textbf{71} (2020), no.~16, 2073--2078.

\end{thebibliography}

% \bibliography{refs}

@@

Illustration of the revised probabilistic model. A pool contains
individuals $\{1,2,3\}$ with state $\theta=(1,1,0)$ (i.e., individuals
1 and 2 are infected). A negative pooled test ($\data=0$) occurs when
three detection paths fail: A false-negative occurs for individuals
$1$ and $2$, each with probability $(1-\sens)$.  Additionally, no
false-positive detection occurs, with probability $\spec$. Individual
$3$ is not infected and does not contribute to the probability of the
pooled test result.
